%-------------------------
% Resume in Latex
% Author : Pragya Datt
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
    \vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/pragya-datt/}{\Large Pragya Datt}} & Email : \href{mailto:pragz01@gmail.com}{pragz01@gmail.com}\\
  \href{https://www.linkedin.com/in/pragya-datt/}{https://www.linkedin.com/in/pragya-datt/} & Mobile : \href{tel:+919711331989}{+919711331989} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NIIT University}{Neemrana, Rajasthan}
      {B.Tech in Computer Science; Specialisation Data Science  CGPA: 9.42}{Aug. 2017 -- Jul. 2021}
    \resumeSubheading
      {Delhi Public School}{Gurgaon, Haryana}
      {CBSE Board, Class 12 (Senior Secondary) - PCM Percentage: 87.6\%}
      {}
      \textit{{CBSE Board, Class 10 (Secondary) - CGPA: 9.8}}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Bigbasket}{Bangalore, KA}
      {Senior Software Engineer}{Oct 2023 - Present}
      \resumeItemListStart
        \resumeItem{Custom Data Setup Framework}
        {
          \begin{itemize} % Nested list
            \item Designed and implemented a complex system framework using a process-task architecture, reducing setup time by 85\%.
            \item 100\% rollout of automated data setup done across all environments for feature testing and deployment.
            \item Developed a reusable template system where tasks (APIs) could be associated with dependencies or be sequenced. 
            \item Implemented JSONPath-based internal associations for managing API inputs/outputs, handling custom functions like "repeat" and "bulk" cases, and supporting file uploads and parsing.
            \item Enhanced scalability and efficiency by enabling templates to be duplicated across environments, streamlining feature testing and reducing setup time.
            \item Managed the project end-to-end, from planning and proposal to development and use case sign-off.
          \end{itemize}
        }
        \resumeItem{Developed Modular Consumer-Producer Flow}
        {
          \begin{itemize} % Nested list
            \item Designed and implemented a modular and reusable consumer-producer flow for a SaaS feature, allowing for seamless addition of new consumers, leading to improved maintainability of the system.
            \item Setup consumers for real-time order activity updates, optimizing the approach to handle multiple topics efficiently without code duplication.
          \end{itemize}
        }
        \resumeItem{Migrated Monolithic (1.0) to Microservice (2.0)}
        {
          \begin{itemize} % Nested list
            \item Successfully planned and executed the migration of features from 1.0 to 2.0, optimizing system architecture and improving overall performance. 
            \item Managed technical specifications, task planning, development, configurations, integration, testing, and release management, contributing to a more efficient and scalable platform.
          \end{itemize}
        }
        \resumeItem{SPOC - ETA Microservice (for BBNow Quick Delivery)}
        {
          \begin{itemize} % Nested list
            \item  Primary contact and lead developer for the heart of quick delivery service that determines delivery times based on store pickers / delivery executives / delivery routes and a variety of configurations and conditional use-cases.
            \item Led  multiple enhancements for complex ETA computations to improve customer perception and app experience.
          \end{itemize}
        }
        \resumeItem{Lead Developer Part of Architect Communities}
        {
          \begin{itemize} % Nested list
            \item Spearheaded critical, tech-heavy and high visibility projects across Bigbasket.
            \item Part of leadership and architect communities to brainstorm and arrive at the best approaches to engineering problems.
          \end{itemize}
        }
      \resumeItemListEnd

    \resumeSubSubheading
    {Software Engineer 2}{ Apr 2022 - Oct 2023}
    \resumeItemListStart
      \resumeItem{Reduced System Errors and Improved Performance}
      {
        \begin{itemize} % Nested list
          \item Accomplished significant performance improvements and reduced 5xx errors by implementing failure handlers, optimizing pod startup times by 50\%, and performing fault injection testing on high-throughput APIs.
          \item  Proactively identified and cleaned up error rates by analyzing Athena queries, deprecating unwanted APIs, and addressing S1 issues through careful non-prod testing and monitoring.
          \item Increased system reliability by adding Aerospike retries to reduce connection timeouts. 
        \end{itemize}
      }
      \resumeItem{Achieved High Code Quality and Test Coverage}
      {
        \begin{itemize} % Nested list
          \item Ensured 90\%+ unit test coverage across projects, validated via PiTest, showcasing a strong commitment to code quality.
          \item Led training sessions on load testing with K6 and introduced automation practices with test containers, Wiremocks, and Mockito, contributing to the team's knowledge growth and improving testing efficiency.
        \end{itemize}
      }
    \resumeItemListEnd

% --------Multiple Positions Heading------------
   \resumeSubSubheading
    {Software Engineer 1}{Jul 2021 - Apr 2022}
    \resumeItemListStart
      \resumeItem{Prime Developer behind BBNow (Quick Delivery)}
      {
        \begin{itemize} % Nested list
          \item  Delivered the heart of the BBNow concept by architecting the ETA microservice (delivery time computation), from boiler plate to release ready code - the most critical piece directly impacting the success of BB.
          \item Achieved impressive results: 150 successful store launches, 18.7 lakh new orders and 71 Cr. in sales within a 5 month period.    
        \end{itemize}
      }
      \resumeItem{Resolved Critical System Issues}
      {
        \begin{itemize} % Nested list
          \item Mitigated a major DDoS attack on BigBasket by proposing and implementing a specialized blocking solution at the network layer, safeguarding system integrity and preventing 2+ hours of downtime.
          \item  Enhanced system performance by introducing targeted caching strategies during SaaS integration, reducing server calls and improving API efficiency.
        \end{itemize}
      }
      \resumeItem{Mentored and Onboarded New Team Members}
      {
        \begin{itemize} % Nested list
          \item Successfully ramped up new developers by conducting KT sessions on functional and technical flows, resulting in faster onboarding and enhanced team productivity.
        \end{itemize}
      }
    \resumeItemListEnd
  %  \resumeSubHeadingListEnd

   \resumeSubSubheading
   {Software Engineer Intern}{Jan 2021 - Jul 2021}
   \resumeItemListStart
      \resumeItem{TATA Digital - BigBasket Member Integration}
      {
        \begin{itemize} % Nested list
          \item Developed and integrated core APIs involving login and authentication for the TATA - BB acquisition period that enabled successful member migration of over 100 million customers.
          \item Worked closely with cross-functional teams, participated in technical discussions, resolved client-side issues.        
          \item Gained exposure to Agile methodologies and SDLC stages.
        \end{itemize}
      }
    \resumeItemListEnd
  % \resumeSubHeadingListEnd
% -------------------------------------------
    \resumeSubheading
      {Tech Mahindra}{Noida, UP}
      {Intern}{May 2019 - Jul 2019}
      \resumeItemListStart
        \item Built a business case modeler tool to test the reliability of RPA products while ensuring business value to TechM customers.
        \item Handled quantitative and qualitative aspects along with data visualization.
        \resumeItem{Technologies}
        {RPA, UiPath, VBA, Advanced Excel, Power BI}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeItem{Student Counseling Chatbot}
      {
        \begin{itemize} % Nested list
          \item Designed and developed a counseling chatbot solution for a career counseling company - deployed live in production.
          \item Recognized as the competition winner, securing a cash prize of INR 50,000 from among 10 finalist teams.
          \item Led the project from start to finish, handling functional and technical requirements, creating a comprehensive system design document, and undertaking full-stack development.
          \item Ensured a seamless user experience with custom UI, multi-device support, and flexible input options.
        \end{itemize}
      }
    \resumeItem{Broke Student Brokers}
      {
        \begin{itemize} % Nested list
          \item Built a cross platform android/ios trading bot app using Flutter to see portfolio and add funds.
          \item Set up serverless functions in python created on Google Cloud that would run everyday at 11AM to forecast and perform trades using Alpaca (Simulated) and Yahoo Finance, Google Firebase as db, Jenkins and Docker to host.
        \end{itemize}
      }

    \resumeItem{Smart India Hackathon - 2020}
      {\textbf{'Grand Finalist' (Top $\mathbf{10\%}$)} - ISRO (Indian Space Research Organization).}

  \resumeSubHeadingListEnd

%
% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
    \textbf{Technologies}{: Kafka, Aerospike, K8s, Jenkins, AWS}
    \hfill
    \textbf{Languages}{: Java, Python, SQL, Javascript}

   }
 \resumeSubHeadingListEnd

%
% --------OTHER ACHIEVEMENTS------------
\section{Other Achievements}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ram Rajindra Malhotra Gold Medal}{Jul 2021}
      {All rounder student in both academics and co-curricular amongst the graduating class.}{}{\textit{Issued by Ram Rajindra Malhotra Education Society}}
    \resumeSubheading
      {Best Sportsperson}{2018-2019}
      {Best sportsperson for the academic year}{}
      {\textit{Issued by NIIT University}}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}